Target Markdown

### 2023-04-26 _targets.Rmd
updated topic model, still need to work on Full_indicator as NAs there create problems + should also look at comp_ind_topics as it seems to generate only NaNs

    tar_target(topic_number,
              find_topic_number(topic_model_input),
                format = "qs"),
    tar_target(topic_model,
               make_topic_model(topic_model_input),
                format = "qs")

@@

     # tar_target(ind_topics,
     #            calc_ind_topics(topic_model = NULL, one_author, ids_complete, db_path), 
     #            format = "qs", pattern = map(one_author), iteration = "list")
     # 
    tar_target(independent_topics,
                comp_ind_topics(independent_pubs))
)

>>>>

    tar_target(topic_number,
              find_topic_number(topic_model_input),
                format = "qs"),
    tar_target(topic_model,
               make_topic_model(topic_model_input, topic_number),
                format = "qs")

@@

     # tar_target(ind_topics,
     #            calc_ind_topics(topic_model = NULL, one_author, ids_complete, db_path), 
     #            format = "qs", pattern = map(one_author), iteration = "list")
     # 
    tar_target(independent_topics,
                comp_ind_topics(independent_pubs, topic_model, db_path))
)
